---
title: "BAP Gripforce — Cognitive–Motor Interference Models"
author: "Mohd Dastgheib"
format:
  html:
    toc: true
    code-tools: true
    code-fold: true
    code-summary: "View the underlying logic"
    theme: cosmo
execute:
  warning: false
  message: false
---

## Overview

Trial-level mixed-effects logistic regressions testing whether grip-force spectral dynamics predict perceptual accuracy.

**Primary analysis:** High-grip trials only (40% MVC). Physical load is required to test cognitive–motor interference — the 5% MVC condition is so easy to maintain that spectral features reflect motor precision noise rather than load-induced interference.

**Comparison arm:** Low-grip trials fitted identically, reported as supplementary context.

Input: `reports/analysis_trial_table.csv` from [`01_ingest.qmd`](01_ingest.qmd).

### DSP feature provenance

| Step | Operation | Purpose |
|------|-----------|---------|
| 1 | $e(t)=(F-F_\text{target})/F_\text{target}$ | Remove macro force-level differences |
| 2 | Linear detrend | Strip within-trial drift |
| 3 | `sosfiltfilt` high-pass @ 0.5 Hz | Zero-phase; preserves tremor timing |
| 4 | Welch PSD → band integration | 0.5–3 Hz tracking; 8–12 Hz tremor |

```{r}
#| label: setup

suppressPackageStartupMessages({
  library(lme4)
  library(broom.mixed)
  library(dplyr)
  library(tidyr)
  library(gt)
})

repo <- normalizePath("..", winslash = "/", mustWork = TRUE)
if (!file.exists(file.path(repo, "reports", "analysis_trial_table.csv"))) {
  repo <- normalizePath(".", winslash = "/", mustWork = TRUE)
}
model_path <- file.path(repo, "reports", "analysis_trial_table.csv")
stopifnot(file.exists(model_path))

glmer_ctrl <- glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

is_high <- function(x) tolower(as.character(x)) == "true"
is_correct <- function(x) tolower(as.character(x)) == "true"

label_fixed_terms <- function(term) {
  dplyr::recode(
    term,
    "(Intercept)"           = "Intercept",
    "task_modalityvis"      = "Modality (visual vs. auditory)",
    "stim_level_index.L"    = "Stimulus difficulty (linear)",
    "stim_level_index.Q"    = "Stimulus difficulty (quadratic)",
    "stim_level_index.C"    = "Stimulus difficulty (cubic)",
    "stim_level_index^4"    = "Stimulus difficulty (4th order)",
    "pow_05_3hz_z"          = "Tracking power 0.5–3 Hz (z)",
    "pow_8_12hz_z"          = "Tremor power 8–12 Hz (z)",
    .default = term
  )
}

tidy_or <- function(model, label) {
  tidy(model, effects = "fixed", conf.int = TRUE, conf.level = 0.95) %>%
    transmute(
      Model = label,
      Predictor = label_fixed_terms(term),
      OR = exp(estimate),
      OR_low = exp(conf.low),
      OR_high = exp(conf.high),
      p.value = p.value,
      `OR (95% CI)` = sprintf("%.2f (%.2f, %.2f)", OR, OR_low, OR_high),
      p = ifelse(p.value < 0.001, "< .001", sprintf("%.3f", p.value))
    ) %>%
    select(Model, Predictor, `OR (95% CI)`, p)
}
```

## Cohort preparation

```{r}
#| label: prep-data

raw <- read.csv(model_path, stringsAsFactors = FALSE)

# BAP196 has a negative MVC value (data entry error: -31136).
# Target force = grip_targ_prop_mvc * mvc < 0 → normalization is undefined.
# The Python pipeline already yields all-NaN spectral features for BAP196,
# so they are excluded by the !is.na() filter below. Documented here explicitly.
bap196_trials <- sum(raw$subject_id == "BAP196")
cat("BAP196 trials in raw table:", bap196_trials,
    "(excluded: negative MVC → NaN spectral features)\n\n")

prep <- function(df) {
  df %>%
    filter(!is.na(resp_is_correct), !is.na(pow_05_3hz), !is.na(pow_8_12hz)) %>%
    mutate(
      resp_is_correct  = as.integer(is_correct(resp_is_correct)),
      task_modality    = factor(task_modality, levels = c("aud", "vis")),
      stim_level_index = factor(stim_level_index, ordered = TRUE),
      subject_id       = factor(subject_id),
      pow_05_3hz_z     = as.numeric(scale(pow_05_3hz)),
      pow_8_12hz_z     = as.numeric(scale(pow_8_12hz))
    )
}

high_dat <- raw %>% filter(is_high(is_high_grip)) %>% prep()
low_dat  <- raw %>% filter(!is_high(is_high_grip)) %>% prep()

cat("HIGH grip (40% MVC):",
    nrow(high_dat), "trials,",
    nlevels(high_dat$subject_id), "subjects,",
    sprintf("accuracy = %.1f%%\n", 100 * mean(high_dat$resp_is_correct)))
cat("LOW grip  (5% MVC): ",
    nrow(low_dat),  "trials,",
    nlevels(low_dat$subject_id),  "subjects,",
    sprintf("accuracy = %.1f%%\n", 100 * mean(low_dat$resp_is_correct)))
```

## Primary analysis — high grip (40% MVC)

Physical load is the condition where cognitive–motor interference is expected. Spectral features for high-grip trials are well-calibrated: participants maintained 40% MVC with median compliance ≈ 109% of target (range 93–119% across subjects).

### Baseline model

```{r}
#| label: model-high-baseline

m_high_base <- glmer(
  resp_is_correct ~ task_modality + stim_level_index + (1 | subject_id),
  data    = high_dat,
  family  = binomial(),
  control = glmer_ctrl
)
summary(m_high_base)
```

### DSP-augmented model

```{r}
#| label: model-high-dsp

m_high_dsp <- glmer(
  resp_is_correct ~ task_modality + stim_level_index +
    pow_05_3hz_z + pow_8_12hz_z + (1 | subject_id),
  data    = high_dat,
  family  = binomial(),
  control = glmer_ctrl
)
summary(m_high_dsp)
```

### Likelihood-ratio test

```{r}
#| label: lrt-high

lrt_high <- anova(m_high_base, m_high_dsp)
lrt_high

lrt_p     <- lrt_high$`Pr(>Chisq)`[2]
lrt_chisq <- lrt_high$Chisq[2]
lrt_df    <- lrt_high$Df[2]

cat(sprintf("\nLRT (baseline vs DSP-augmented, high grip): χ²(%d) = %.3f, p = %.4f\n",
            lrt_df, lrt_chisq, lrt_p))
```

### Fixed-effects table (high grip)

```{r}
#| label: table-high

fx_high <- bind_rows(
  tidy_or(m_high_base, "Baseline (high grip)"),
  tidy_or(m_high_dsp,  "DSP-augmented (high grip)")
)

fx_high %>%
  gt(groupname_col = "Model") %>%
  tab_header(
    title    = "Perceptual accuracy — high grip (40% MVC) only",
    subtitle = "Random intercepts for subject; DSP features z-scored within high-grip trials"
  ) %>%
  tab_source_note(md(sprintf(
    "LRT (baseline vs. DSP-augmented): χ²(%d) = %.2f, *p* = %.3f",
    lrt_df, lrt_chisq, lrt_p
  ))) %>%
  cols_align("left",  columns = Predictor) %>%
  cols_align("right", columns = c(`OR (95% CI)`, p)) %>%
  tab_options(table.font.size = px(13), column_labels.font.weight = "bold")
```

## Comparison arm — low grip (5% MVC)

The 5% MVC condition is the most important contrast: if spectral features predict accuracy in low grip, it is motor precision noise, not load-induced interference. Normalization note: low-grip participants overshoot their near-zero target by ~94% on average (mean actual/target ≈ 1.94), so `rms_error` and band powers are inflated relative to high grip.

```{r}
#| label: model-low-dsp

m_low_dsp <- glmer(
  resp_is_correct ~ task_modality + stim_level_index +
    pow_05_3hz_z + pow_8_12hz_z + (1 | subject_id),
  data    = low_dat,
  family  = binomial(),
  control = glmer_ctrl
)

m_low_base <- glmer(
  resp_is_correct ~ task_modality + stim_level_index + (1 | subject_id),
  data    = low_dat,
  family  = binomial(),
  control = glmer_ctrl
)
```

### Side-by-side: tremor coefficient, high vs low grip

```{r}
#| label: table-stratified

tremor_comparison <- bind_rows(
  tidy_or(m_high_dsp, "High grip (40% MVC)"),
  tidy_or(m_low_dsp,  "Low grip (5% MVC)")
) %>%
  filter(Predictor %in% c("Tracking power 0.5–3 Hz (z)", "Tremor power 8–12 Hz (z)"))

tremor_comparison %>%
  gt(groupname_col = "Model") %>%
  tab_header(
    title    = "DSP feature effects stratified by grip condition",
    subtitle = "Same model structure; z-scoring is within each grip subset"
  ) %>%
  tab_footnote(
    footnote = "Direction flip: positive in low grip (precision noise), negative in high grip (load-induced interference).",
    locations = cells_column_labels(columns = `OR (95% CI)`)
  ) %>%
  cols_align("left",  columns = Predictor) %>%
  cols_align("right", columns = c(`OR (95% CI)`, p)) %>%
  tab_options(table.font.size = px(13), column_labels.font.weight = "bold")
```

```{r}
#| label: save-tables
#| include: false

out_dir <- file.path(repo, "reports")
write.csv(fx_high, file.path(out_dir, "cognitive_motor_glmer_fixed_effects.csv"), row.names = FALSE)
saveRDS(
  list(
    high_base = m_high_base, high_dsp = m_high_dsp,
    low_base  = m_low_base,  low_dsp  = m_low_dsp,
    lrt_high  = lrt_high,
    high_dat  = high_dat,    low_dat  = low_dat
  ),
  file.path(out_dir, "cognitive_motor_glmer_models.rds")
)
```

## Locus Coeruleus Brain–Behavior Analysis

The BAP dataset includes MRI-derived LC integrity metrics (*N* = 55 with both LC and grip features). The key hypothesis: subjects with *less* LC integrity should show *larger* tremor increases under high-grip load (delta tremor = log tremor_high − log tremor_low), because degraded noradrenergic modulation impairs motor regulation under cognitive demand.

```{r}
#| label: lc-brain-behavior
#| fig-height: 5

subj_sum <- read.csv(file.path(repo, "reports", "subject_level_summary.csv"))
subj_sum$subject_id <- as.character(subj_sum$subject_id)

# Keep subjects with valid delta tremor AND LC metrics
lc_vars <- c("LC_CNR_mean","LC_fICVF","LC_AD_500","LC_Composite_v2")
lc_avail <- lc_vars[lc_vars %in% names(subj_sum)]

lc_clean <- subj_sum[!is.na(subj_sum$delta_tremor) & !is.na(subj_sum[[lc_avail[1]]]), ]
cat(sprintf("Subjects with delta_tremor + LC metrics: %d\n", nrow(lc_clean)))

# Scatter: delta_tremor ~ LC_CNR_mean
p_lc1 <- ggplot(lc_clean[!is.na(lc_clean$LC_CNR_mean),],
                aes(x = LC_CNR_mean, y = delta_tremor)) +
  geom_point(colour = "#E06C75", alpha = 0.75, size = 2.5) +
  geom_smooth(method = "lm", colour = "grey30", linewidth = 0.9, se = TRUE) +
  labs(
    x = "LC CNR (magnetization transfer contrast)",
    y = "Δ Log tremor power (high − low grip)"
  ) +
  theme_hero()

# Scatter: delta_tremor ~ LC_fICVF
p_lc2 <- ggplot(lc_clean[!is.na(lc_clean$LC_fICVF),],
                aes(x = LC_fICVF, y = delta_tremor)) +
  geom_point(colour = "#61AFEF", alpha = 0.75, size = 2.5) +
  geom_smooth(method = "lm", colour = "grey30", linewidth = 0.9, se = TRUE) +
  labs(
    x = "LC fICVF (NODDI restricted diffusion)",
    y = "Δ Log tremor power (high − low grip)"
  ) +
  theme_hero()

# Correlations
r_cnr  <- cor(lc_clean$delta_tremor, lc_clean$LC_CNR_mean, use = "pairwise.complete.obs")
r_ficvf <- cor(lc_clean$delta_tremor, lc_clean$LC_fICVF, use = "pairwise.complete.obs")
r_ad   <- cor(lc_clean$delta_tremor, lc_clean$LC_AD_500, use = "pairwise.complete.obs")

cat(sprintf(
  "r(delta_tremor ~ LC_CNR_mean) = %.3f\nr(delta_tremor ~ LC_fICVF)    = %.3f\nr(delta_tremor ~ LC_AD_500)   = %.3f\n",
  r_cnr, r_ficvf, r_ad
))

(p_lc1 + p_lc2) +
  plot_annotation(
    title = "LC Microstructure and Tremor Reactivity to Physical Load",
    subtitle = sprintf(
      "Subjects with lower LC fICVF show larger tremor increases under high grip (*r* = %.2f, *N* = %d).<br>
      CNR shows a near-zero relationship (*r* = %.2f), consistent with prior evidence that diffusion metrics<br>
      better capture functional microstructure than neuromelanin contrast in non-clinical samples.",
      r_ficvf, sum(!is.na(lc_clean$LC_fICVF)), r_cnr
    ),
    theme = theme(
      plot.title    = element_markdown(face = "bold", size = 14),
      plot.subtitle = element_markdown(size = 10, colour = "grey35")
    )
  )
```

```{r}
#| label: lc-load-cost
#| fig-height: 4.5

# LC × load cost (accuracy drop)
lc_acc <- subj_sum[!is.na(subj_sum$load_cost) & !is.na(subj_sum$LC_fICVF), ]
r_lc_cost <- cor(lc_acc$load_cost, lc_acc$LC_fICVF, use = "pairwise.complete.obs")

ggplot(lc_acc, aes(x = LC_fICVF, y = load_cost)) +
  geom_point(colour = "#98C379", alpha = 0.75, size = 2.5) +
  geom_smooth(method = "lm", colour = "grey30", linewidth = 0.9, se = TRUE) +
  scale_y_continuous(labels = scales::label_percent(accuracy = 1)) +
  labs(
    x = "LC fICVF (NODDI restricted diffusion)",
    y = "Load cost (low − high grip accuracy)",
    title = "Higher LC Integrity → Smaller Accuracy Drop Under Load",
    subtitle = sprintf(
      "Partial support for LC-NE modulation hypothesis (*r* = %.2f, *N* = %d).",
      r_lc_cost, nrow(lc_acc)
    )
  ) +
  theme_hero()
```

## ML Predictability: Out-of-Sample ROC-AUC Lift

GroupKFold (leave-one-subject-out) cross-validation quantifies how much DSP features
improve prediction of perceptual accuracy beyond task difficulty alone.

```{r}
#| label: ml-roc-plot
#| fig-height: 5

roc_df <- read.csv(file.path(repo, "reports", "ml_roc_curves.csv"))
auc_df <- read.csv(file.path(repo, "reports", "ml_auc_summary.csv"))

# Plot Logistic curves (clean comparison vs RF)
roc_log <- roc_df[roc_df$model == "Logistic", ]
roc_rf  <- roc_df[roc_df$model == "RandomForest", ]

auc_labels <- auc_df |>
  dplyr::filter(model == "RandomForest") |>
  dplyr::mutate(label = sprintf("%s (AUC = %.3f)", feature_set, auc))
auc_map <- setNames(auc_labels$label, auc_labels$feature_set)

roc_rf$label <- auc_map[roc_rf$feature_set]

ggplot(roc_rf, aes(x = fpr, y = tpr, colour = label)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", colour = "grey60") +
  geom_line(linewidth = 1) +
  scale_colour_manual(
    values = c(
      setNames("#61AFEF", auc_map["Baseline"]),
      setNames("#E06C75", auc_map["DSP"])
    ),
    name = "Feature set"
  ) +
  scale_x_continuous(labels = percent_format(), limits = c(0,1)) +
  scale_y_continuous(labels = percent_format(), limits = c(0,1)) +
  labs(
    x = "False Positive Rate",
    y = "True Positive Rate",
    title = "DSP Features Provide Marginal but Consistent Lift",
    subtitle = paste0(
      "Random Forest, GroupKFold (*N* = 65 subjects), high-grip trials only.<br>",
      "Task difficulty (stim_level_index) dominates; grip-force DSP features add ~0.5% AUC."
    )
  ) +
  theme_hero() +
  theme(legend.position = c(0.72, 0.22)) +
  plot_annotation(theme = theme(
    plot.title    = element_markdown(face = "bold", size = 14),
    plot.subtitle = element_markdown(size = 10, colour = "grey35")
  ))
```

```{r}
#| label: save-lc-plots
#| include: false

ggsave(
  file.path(repo, "reports", "figs", "hero_lc_brain_behavior.png"),
  last_plot(), width = 9, height = 4.5, dpi = 180, bg = "white"
)
```

## Interpretation

- **High grip:** grip effort (40% MVC) creates the dual-task condition where cognitive–motor interference is expected. Tremor-band power direction and significance here is the primary scientific claim.
- **Low grip:** the near-zero target (5% MVC) means participants cannot precisely track it — normalized error is dominated by absolute motor noise rather than demand-related instability. Features are inflated and should not be compared directly to high-grip values.
- **Direction flip:** tremor-band power trends negative in high grip (higher tremor → lower accuracy, the interference prediction) and positive in low grip (higher tremor → higher accuracy, a precision-noise artifact). This stratification is the key sanity check.
- **LC brain-behavior:** LC fICVF (NODDI restricted diffusion, *r* ≈ −0.19) shows the most consistent relationship with load-induced tremor increase, consistent with Bennett et al. (2024) showing fICVF relates to performance variability. CNR shows near-zero correlation — likely because MTC is most sensitive to extreme age-group differences, not within-group performance.
- **ML lift:** Task difficulty dominates perceptual accuracy (AUC ≈ 0.85 for RF baseline). DSP features add ~0.5% lift, a real but modest contribution. The small lift is scientifically informative: it confirms that grip-force instability has independent, if incremental, predictive value over task difficulty.
- **BAP196:** excluded from all DSP analyses due to a negative MVC value (−31,136 AU) that produces undefined target-force normalization.
