---
title: "BAP Gripforce — Hero Visualizations"
author: "Mohd Dastgheib"
format:
  html:
    toc: true
    code-tools: true
    code-fold: true
    code-summary: "View the underlying logic"
    theme: cosmo
    fig-width: 9
    fig-height: 10
execute:
  warning: false
  message: false
fig-format: png
fig-dpi: 180
---

## Overview

Portfolio-grade figures for quantitative UX / human-factors audiences:

1. **Single-trial signal chain** — time domain (force → error → instability) **+ Welch PSD** with tracking/tremor bands highlighted.
2. **Probe-locked spectrogram** — time × frequency heatmap aligned to oddball onset (*t* = 0 at probe).
3. **Population spectral fingerprint** — band-power distributions by grip effort and accuracy.
4. **Behavioral lift** — adjusted accuracy as a function of tremor-band power, split by grip effort.

Inputs: `reports/analysis_trial_table.csv` plus raw grip CSVs via `config/paths.local.yaml`. Welch PSD for the hero trial is computed in Python (`scripts/export_hero_psd.py`) to match the ingest pipeline exactly.

```{r}
#| label: install-packages
#| eval: false

install.packages(c(
  "ggplot2", "patchwork", "ggtext", "dplyr", "tidyr",
  "scales", "lme4", "yaml", "stringr", "plotly", "htmlwidgets"
))
```

```{r}
#| label: setup

suppressPackageStartupMessages({
  library(ggplot2)
  library(patchwork)
  library(ggtext)
  library(dplyr)
  library(tidyr)
  library(scales)
  library(lme4)
  library(yaml)
  library(stringr)
})

has_plotly <- requireNamespace("plotly", quietly = TRUE) &&
  requireNamespace("htmlwidgets", quietly = TRUE)

repo <- normalizePath("..", winslash = "/", mustWork = TRUE)
if (!file.exists(file.path(repo, "reports", "analysis_trial_table.csv"))) {
  repo <- normalizePath(".", winslash = "/", mustWork = TRUE)
}

config_path <- file.path(repo, "config", "paths.local.yaml")
if (!file.exists(config_path)) {
  config_path <- file.path(repo, "config", "paths.example.yaml")
}
paths <- read_yaml(config_path)
grip_root <- paths[["gripforce_root"]]
model_path <- file.path(repo, "reports", "analysis_trial_table.csv")
fig_dir <- file.path(repo, "reports", "figures")
dir.create(fig_dir, recursive = TRUE, showWarnings = FALSE)

fs_hz <- 100
trial_epoch_s <- 2.94
probe_window_s <- 0.15
tracking_band <- c(0.5, 3.0)
tremor_band <- c(8.0, 12.0)

band_colors <- c(
  "Tracking\n0.5–3 Hz" = "#009E73",
  "Tremor\n8–12 Hz" = "#CC79A7"
)

okabe <- c(
  "Low effort" = "#0072B2",
  "High effort" = "#D55E00"
)

theme_hero <- function(base_size = 12) {
  theme_minimal(base_size = base_size) +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.major.y = element_line(color = "grey90", linewidth = 0.35),
      plot.title = element_markdown(face = "bold", size = rel(1.15), hjust = 0),
      plot.subtitle = element_markdown(color = "grey35", size = rel(0.95), hjust = 0),
      plot.caption = element_text(color = "grey45", size = rel(0.78), hjust = 0),
      axis.title = element_text(color = "grey15", face = "plain"),
      axis.text = element_text(color = "grey25"),
      legend.position = "top",
      legend.title = element_blank(),
      plot.margin = margin(12, 16, 12, 12)
    )
}

probe_onset_s <- function(meta_row) {
  if ("probe_onset_s" %in% names(meta_row)) meta_row$probe_onset_s else meta_row$stim_offset
}

band_rect <- function(fmin, fmax, fill, alpha = 0.22) {
  annotate("rect", xmin = fmin, xmax = fmax, ymin = -Inf, ymax = Inf, fill = fill, alpha = alpha)
}
probe_rect <- function(stim_onset_s, width_s = probe_window_s) {
  annotate(
    "rect",
    xmin = stim_onset_s,
    xmax = stim_onset_s + width_s,
    ymin = -Inf,
    ymax = Inf,
    fill = "#FFB000",
    alpha = 0.18
  )
}

# (band_rect defined above)

panel_tag <- function(label) {
  annotate(
    "text",
    x = -Inf, y = Inf,
    label = label,
    hjust = -0.15, vjust = 1.35,
    fontface = "bold",
    size = 4.2,
    color = "grey20"
  )
}

rolling_var <- function(x, window = 31) {
  n <- length(x)
  half <- window %/% 2
  vapply(seq_len(n), function(i) {
    lo <- max(1L, i - half)
    hi <- min(n, i + half)
    stats::var(x[lo:hi], na.rm = TRUE)
  }, numeric(1))
}

find_grip_file <- function(subject_id, session_num, run_num, task, root) {
  pattern <- sprintf(
    "subject%s_%s_session%s_run%s_.*_gripforce\\.csv",
    subject_id, task, session_num, run_num
  )
  hits <- list.files(root, pattern = pattern, full.names = TRUE, recursive = TRUE)
  if (length(hits) == 0) {
    stop("No gripforce file found for ", subject_id, " ", task, " session ", session_num)
  }
  hits[[1]]
}

load_trial_trace <- function(
    subject_id,
    session_num,
    run_num,
    trial_idx,
    task,
    mvc,
    grip_targ_prop_mvc,
    stim_offset_s,
    root = grip_root,
    fs = fs_hz,
    min_rows_per_trial = 100) {
  path <- find_grip_file(subject_id, session_num, run_num, task, root)
  raw <- read.csv(
    path,
    header = FALSE,
    col.names = c("marker", "elapsed_time", "abs_time", "raw_force")
  )

  task_upper <- toupper(task)
  raw$grip_force_au <- if (task_upper %in% c("AODDBALL", "VODDBALL")) {
    raw$marker
  } else {
    raw$raw_force
  }

  raw$epoch_idx <- cumsum(c(1, diff(raw$elapsed_time) < 0))
  counts <- raw %>%
    count(epoch_idx, name = "n_rows")
  keep_epochs <- counts %>%
    filter(n_rows >= min_rows_per_trial) %>%
    arrange(epoch_idx) %>%
    mutate(trial_idx = row_number())

  trial <- raw %>%
    inner_join(keep_epochs %>% select(epoch_idx, trial_idx), by = "epoch_idx") %>%
    filter(trial_idx == !!trial_idx) %>%
    arrange(elapsed_time)

  if (nrow(trial) < 50) {
    stop(
      "Trial ", trial_idx, " in ", basename(path),
      " has too few samples after segmentation (", nrow(trial), ")."
    )
  }

  trial$t_rel_s <- trial$elapsed_time - trial$elapsed_time[1]
  target_force <- grip_targ_prop_mvc * mvc
  trial$target_force <- target_force
  trial$normalized_error <- (trial$grip_force_au - target_force) / target_force
  trial$rolling_var <- rolling_var(trial$normalized_error, window = 31)
  trial$stim_onset_s <- stim_offset_s

  trial
}
```

## Visual 1 — Single-trial anatomy (time domain)

```{r}
#| label: visual-1-data

model_tbl <- read.csv(model_path, stringsAsFactors = FALSE)

hero_meta <- model_tbl %>%
  filter(
    task_modality == "vis",
    tolower(as.character(is_high_grip)) == "true",
    tolower(as.character(resp_is_correct)) == "false",
    !is.na(pow_8_12hz)
  ) %>%
  arrange(desc(pow_8_12hz)) %>%
  slice(1)

trace <- load_trial_trace(
  subject_id = hero_meta$subject_id,
  session_num = hero_meta$session_num,
  run_num = hero_meta$run_num,
  trial_idx = hero_meta$trial_idx,
  task = hero_meta$task,
  mvc = hero_meta$mvc,
  grip_targ_prop_mvc = hero_meta$grip_targ_prop_mvc,
  stim_offset_s = hero_meta$probe_onset_s   # seconds into trial; NOT stim_offset for aud
)

trace_label <- sprintf(
  "%s · %s · session %s · trial %s · incorrect response",
  hero_meta$subject_id,
  hero_meta$task_modality,
  hero_meta$session_num,
  hero_meta$trial_idx
)

hero_onset <- probe_onset_s(hero_meta)

# Export hero metadata for Python PSD computation (matches ingest pipeline)
hero_meta_path <- file.path(fig_dir, "_hero_meta.csv")
hero_psd_path <- file.path(fig_dir, "_hero_psd.csv")
write.csv(hero_meta, hero_meta_path, row.names = FALSE)

py_script <- file.path(repo, "scripts", "export_hero_psd.py")
py_cmd <- sprintf(
  "python3 %s %s %s",
  shQuote(py_script),
  shQuote(hero_meta_path),
  shQuote(hero_psd_path)
)
py_status <- system(py_cmd, intern = FALSE)
if (py_status != 0) {
  stop("Python PSD export failed. Run from repo root with python3 + scipy available.")
}

hero_psd <- read.csv(hero_psd_path)
hero_psd_log <- hero_psd %>%
  filter(freq_hz > 0) %>%
  mutate(psd_log10 = log10(pmax(psd, .Machine$double.xmin)))

hero_spec_path <- file.path(fig_dir, "_hero_spectrogram.csv")
hero_spec <- read.csv(hero_spec_path) %>%
  filter(freq_hz <= 20, power > 0) %>%
  mutate(power_db = 10 * log10(power))

trace_probe <- trace %>%
  mutate(t_from_probe = t_rel_s - hero_onset)
```

```{r}
#| label: visual-1-anatomy
#| fig-cap: "Single-trial signal chain: time domain (A–C) and Welch PSD (D) with DSP bands highlighted."

p_force <- ggplot(trace, aes(x = t_rel_s, y = grip_force_au)) +
  geom_line(color = "#0072B2", linewidth = 0.75) +
  geom_hline(
    yintercept = hero_meta$grip_targ_prop_mvc * hero_meta$mvc,
    linetype = "dashed",
    color = "#999999",
    linewidth = 0.45
  ) +
  probe_rect(hero_onset) +
  panel_tag("A") +
  scale_x_continuous(limits = c(0, trial_epoch_s), expand = c(0, 0)) +
  labs(x = NULL, y = "Grip force (a.u.)") +
  theme_hero()

p_error <- ggplot(trace, aes(x = t_rel_s, y = normalized_error)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "#666666", linewidth = 0.45) +
  geom_line(color = "#009E73", linewidth = 0.75) +
  probe_rect(hero_onset) +
  panel_tag("B") +
  scale_x_continuous(limits = c(0, trial_epoch_s), expand = c(0, 0)) +
  labs(x = NULL, y = "Normalized error") +
  theme_hero()

p_instability <- ggplot(trace, aes(x = t_rel_s, y = rolling_var)) +
  geom_line(color = "#D55E00", linewidth = 0.8) +
  probe_rect(hero_onset) +
  panel_tag("C") +
  scale_x_continuous(limits = c(0, trial_epoch_s), expand = c(0, 0)) +
  scale_y_continuous(labels = label_number(accuracy = 0.001)) +
  labs(x = "Time within trial (s)", y = "Rolling variance") +
  theme_hero()

p_psd <- ggplot(hero_psd_log, aes(x = freq_hz, y = psd_log10)) +
  band_rect(tracking_band[1], tracking_band[2], band_colors[[1]]) +
  band_rect(tremor_band[1], tremor_band[2], band_colors[[2]]) +
  geom_vline(xintercept = c(tracking_band, tremor_band), color = "grey70", linewidth = 0.3, linetype = "dotted") +
  geom_line(color = "#332288", linewidth = 0.85) +
  panel_tag("D") +
  scale_x_continuous(limits = c(0, 20), breaks = seq(0, 20, 5), expand = c(0, 0)) +
  labs(
    x = "Frequency (Hz)",
    y = expression(log[10] ~ PSD)
  ) +
  annotate(
    "text",
    x = 1.5, y = max(hero_psd_log$psd_log10) * 0.95,
    label = "Tracking\n0.5–3 Hz",
    color = band_colors[[1]], size = 3.2, fontface = "bold", hjust = 0
  ) +
  annotate(
    "text",
    x = 10, y = max(hero_psd_log$psd_log10) * 0.95,
    label = "Tremor\n8–12 Hz",
    color = band_colors[[2]], size = 3.2, fontface = "bold", hjust = 0
  ) +
  theme_hero()

fig_anatomy <- (p_force / p_error / p_instability) | p_psd +
  plot_layout(widths = c(1.2, 1)) +
  plot_annotation(
    title = "The Signal Chain: From Grip Force to Spectral Phenotype",
    subtitle = paste0(
      trace_label,
      "<br>Time panels: probe onset at *t* = ",
      format(hero_onset, nsmall = 2),
      " s (orange band). **D**: Welch PSD after target-normalization, detrend, and 0.5 Hz zero-phase high-pass."
    ),
    theme = theme(
      plot.title = element_markdown(face = "bold", size = 16, hjust = 0),
      plot.subtitle = element_markdown(size = 10.5, color = "grey35", hjust = 0)
    )
  )

fig_anatomy
```

```{r}
#| label: visual-1-anatomy-interactive
#| eval: !expr 'has_plotly && knitr::is_html_output()'

if (has_plotly) {
  plotly::subplot(
    plotly::ggplotly(p_force, tooltip = "text") %>%
      plotly::layout(hovermode = "x unified"),
    plotly::ggplotly(p_error, tooltip = "text") %>%
      plotly::layout(hovermode = "x unified"),
    plotly::ggplotly(p_instability, tooltip = "text") %>%
      plotly::layout(hovermode = "x unified"),
    nrows = 3,
    shareX = TRUE,
    titleY = TRUE
  ) %>%
    plotly::layout(
      title = list(
        text = paste0(
          "Single-Trial Grip Dynamics During Perceptual Decision<br>",
          "<sup>", trace_label, " · hover to inspect time points</sup>"
        ),
        x = 0.01,
        xanchor = "left"
      ),
      showlegend = FALSE
    )
}
```

```{r}
#| label: save-visual-1
#| include: false

ggsave(
  file.path(fig_dir, "hero_single_trial_anatomy.png"),
  fig_anatomy,
  width = 11,
  height = 9,
  dpi = 180,
  bg = "white"
)
```

## Visual 4 — Probe-locked spectrogram (cognitive shock)

Time–frequency power aligned so **probe onset = 0 s**. Pre-probe window shaded; tracking and tremor bands highlighted. Top panel shows normalized error on the same axis — the motor response to the perceptual event.

```{r}
#| label: visual-4-specgram
#| fig-cap: "Probe-locked spectrogram with normalized error aligned to oddball onset."

pre_probe_fill <- "#404040"

p_probe_error <- ggplot(trace_probe, aes(x = t_from_probe, y = normalized_error)) +
  annotate("rect", xmin = -Inf, xmax = 0, ymin = -Inf, ymax = Inf, fill = pre_probe_fill, alpha = 0.07) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey55", linewidth = 0.4) +
  geom_vline(xintercept = 0, color = "#FFB000", linewidth = 0.85) +
  geom_line(color = "#009E73", linewidth = 0.8) +
  panel_tag("A") +
  scale_x_continuous(limits = c(-0.25, 2.4), expand = c(0, 0)) +
  labs(x = NULL, y = "Normalized error") +
  theme_hero()

db_limits <- quantile(hero_spec$power_db, c(0.05, 0.98), na.rm = TRUE)

p_specgram <- ggplot(hero_spec, aes(x = time_from_probe_s, y = freq_hz, fill = power_db)) +
  annotate("rect", xmin = -Inf, xmax = 0, ymin = -Inf, ymax = Inf, fill = pre_probe_fill, alpha = 0.18) +
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = tracking_band[1], ymax = tracking_band[2],
           fill = band_colors[[1]], alpha = 0.12) +
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = tremor_band[1], ymax = tremor_band[2],
           fill = band_colors[[2]], alpha = 0.12) +
  geom_raster(interpolate = TRUE) +
  geom_vline(xintercept = 0, color = "white", linewidth = 0.7, linetype = "dashed") +
  panel_tag("B") +
  scale_fill_viridis_c(
    option = "magma",
    name = "Power (dB)",
    limits = db_limits,
    oob = scales::squish
  ) +
  scale_x_continuous(limits = c(-0.25, 2.4), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0, 20), expand = c(0, 0), breaks = seq(0, 20, 5)) +
  labs(
    x = "Time from probe onset (s)",
    y = "Frequency (Hz)"
  ) +
  theme_hero() +
  theme(legend.key.height = unit(0.9, "cm"))

fig_specgram <- p_probe_error / p_specgram +
  plot_layout(heights = c(1, 2.4)) +
  plot_annotation(
    title = "The Cognitive Shock: Probe-Locked Motor Spectrogram",
    subtitle = paste0(
      trace_label,
      "<br>**A** = normalized error; **B** = short-time spectrum. Vertical gold line = oddball probe (*t* = 0). ",
      "Grey shading = pre-probe baseline. Green band = tracking (0.5–3 Hz); pink band = tremor (8–12 Hz)."
    ),
    theme = theme(
      plot.title = element_markdown(face = "bold", size = 16, hjust = 0),
      plot.subtitle = element_markdown(size = 10.5, color = "grey35", hjust = 0)
    )
  )

fig_specgram
```

```{r}
#| label: visual-4-specgram-interactive
#| eval: !expr 'has_plotly && knitr::is_html_output()'

if (has_plotly) {
  plotly::ggplotly(p_specgram, tooltip = c("x", "y", "fill")) %>%
    plotly::layout(
      title = "Probe-locked spectrogram (hover to inspect frequency bursts)",
      xaxis = list(title = "Time from probe onset (s)"),
      yaxis = list(title = "Frequency (Hz)")
    )
}
```

```{r}
#| label: save-visual-4
#| include: false

ggsave(
  file.path(fig_dir, "hero_probe_locked_spectrogram.png"),
  fig_specgram,
  width = 10,
  height = 7,
  dpi = 180,
  bg = "white"
)
```

## Visual 2 — Population spectral fingerprint

Trial-level band powers from the full analysis cohort, split by grip effort and perceptual outcome.

```{r}
#| label: visual-spectral-pop-data

spec_dat <- model_tbl %>%
  filter(
    !is.na(pow_05_3hz), !is.na(pow_8_12hz), !is.na(resp_is_correct),
    pow_05_3hz > 0, pow_8_12hz > 0
  ) %>%
  mutate(
    grip_effort = ifelse(
      tolower(as.character(is_high_grip)) == "true",
      "High effort", "Low effort"
    ),
    outcome = ifelse(
      tolower(as.character(resp_is_correct)) == "true",
      "Correct", "Incorrect"
    ),
    grip_effort = factor(grip_effort, levels = c("Low effort", "High effort")),
    outcome = factor(outcome, levels = c("Correct", "Incorrect")),
    log_tracking = log10(pow_05_3hz),
    log_tremor = log10(pow_8_12hz)
  )

spec_long <- spec_dat %>%
  select(grip_effort, outcome, log_tracking, log_tremor) %>%
  pivot_longer(
    cols = c(log_tracking, log_tremor),
    names_to = "band",
    values_to = "log_power"
  ) %>%
  mutate(
    band = recode(
      band,
      log_tracking = "Tracking (0.5–3 Hz)",
      log_tremor = "Tremor (8–12 Hz)"
    )
  )
```

```{r}
#| label: visual-spectral-pop
#| fig-cap: "Population distribution of log10 band power by grip effort and perceptual outcome."

p_spec_violin <- ggplot(spec_long, aes(x = outcome, y = log_power, fill = outcome)) +
  geom_violin(trim = FALSE, alpha = 0.35, color = NA) +
  geom_boxplot(width = 0.14, outlier.size = 0.4, alpha = 0.85, color = "grey25") +
  facet_grid(band ~ grip_effort, scales = "free_y") +
  scale_fill_manual(values = c("Correct" = "#009E73", "Incorrect" = "#D55E00")) +
  scale_y_continuous(limits = c(-7, 0), breaks = seq(-6, 0, 2)) +
  labs(
    title = "Spectral Phenotype of Cognitive–Motor Interference",
    subtitle = paste0(
      "Trial-level band power across the analysis cohort (n = ",
      format(nrow(spec_dat), big.mark = ","),
      " trials with non-zero band power)"
    ),
    x = NULL,
    y = expression(log[10] ~ "band power"),
    caption = "Tracking band = visuomotor control; tremor band = physiological instability. Powers from target-normalized, filtered Welch PSD."
  ) +
  theme_hero() +
  theme(legend.position = "none", strip.text = element_text(face = "bold"))

p_spec_violin
```

```{r}
#| label: visual-spectral-scatter
#| fig-cap: "Feature space: tracking vs tremor band power, colored by accuracy."

p_spec_scatter <- ggplot(spec_dat, aes(x = log_tracking, y = log_tremor, color = outcome)) +
  geom_point(alpha = 0.25, size = 1.2) +
  geom_density2d(color = "grey55", linewidth = 0.4, bins = 5) +
  facet_wrap(~ grip_effort) +
  scale_color_manual(values = c("Correct" = "#009E73", "Incorrect" = "#D55E00")) +
  scale_x_continuous(limits = c(-5, 0)) +
  scale_y_continuous(limits = c(-6, -2)) +
  labs(
    title = "Two-Band Feature Space",
    subtitle = "Each point is one trial; contours show density. Errors cluster toward higher tremor under load.",
    x = expression(log[10] ~ "tracking power (0.5–3 Hz)"),
    y = expression(log[10] ~ "tremor power (8–12 Hz)"),
    color = "Outcome"
  ) +
  theme_hero()

p_spec_scatter
```

```{r}
#| label: save-visual-spectral
#| include: false

ggsave(
  file.path(fig_dir, "hero_spectral_fingerprint.png"),
  p_spec_violin,
  width = 9,
  height = 6,
  dpi = 180,
  bg = "white"
)
ggsave(
  file.path(fig_dir, "hero_spectral_feature_space.png"),
  p_spec_scatter,
  width = 9,
  height = 4.5,
  dpi = 180,
  bg = "white"
)
```

## Visual 3 — Behavioral lift (DSP × effort)

Adjusted marginal accuracy from a mixed model with tremor × grip interaction, controlling for modality and difficulty.

```{r}
#| label: visual-2-data

viz_dat <- model_tbl %>%
  filter(
    !is.na(resp_is_correct),
    !is.na(pow_8_12hz),
    !is.na(pow_05_3hz)
  ) %>%
  mutate(
    resp_is_correct = as.integer(tolower(as.character(resp_is_correct)) == "true"),
    task_modality = factor(task_modality, levels = c("aud", "vis")),
    stim_level_index = factor(stim_level_index, ordered = TRUE),
    grip_effort = factor(
      tolower(as.character(is_high_grip)) == "true",
      levels = c(FALSE, TRUE),
      labels = c("Low effort", "High effort")
    ),
    subject_id = factor(subject_id),
    tremor_z = as.numeric(scale(pow_8_12hz))
  )

glmer_ctrl <- glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

m_lift <- glmer(
  resp_is_correct ~ tremor_z * grip_effort + task_modality + stim_level_index +
    (1 | subject_id),
  data = viz_dat,
  family = binomial(),
  control = glmer_ctrl
)

tremor_grid <- seq(-2, 2, length.out = 60)
pred_grid <- expand.grid(
  tremor_z = tremor_grid,
  grip_effort = levels(viz_dat$grip_effort),
  task_modality = "vis",
  stim_level_index = factor(2, levels = levels(viz_dat$stim_level_index), ordered = TRUE),
  KEEP.OUT.ATTRS = FALSE,
  stringsAsFactors = FALSE
)
pred_grid$grip_effort <- factor(pred_grid$grip_effort, levels = levels(viz_dat$grip_effort))
pred_grid$task_modality <- factor(pred_grid$task_modality, levels = levels(viz_dat$task_modality))

pred_grid$pred_acc <- predict(m_lift, newdata = pred_grid, type = "response", re.form = NA)

# Empirical bins for overlay
viz_bins <- viz_dat %>%
  mutate(tremor_bin = cut(
    tremor_z,
    breaks = seq(-2.5, 2.5, by = 1),
    labels = c("< −1.5", "−1.5 to −0.5", "−0.5 to 0.5", "0.5 to 1.5", "> 1.5")
  )) %>%
  group_by(grip_effort, tremor_bin) %>%
  summarise(
    acc = mean(resp_is_correct),
    se = sqrt(acc * (1 - acc) / n()),
    tremor_mid = mean(tremor_z),
    n = n(),
    .groups = "drop"
  ) %>%
  filter(n >= 25)
```

```{r}
#| label: visual-2-lift
#| fig-cap: "Population-level accuracy as a function of tremor-band power, split by grip effort."

fig_lift <- ggplot() +
  geom_line(
    data = pred_grid,
    aes(x = tremor_z, y = pred_acc, color = grip_effort, linewidth = grip_effort)
  ) +
  geom_pointrange(
    data = viz_bins,
    aes(x = tremor_mid, y = acc, ymin = pmax(acc - 1.96 * se, 0), ymax = pmin(acc + 1.96 * se, 1),
        color = grip_effort),
    linewidth = 0.35,
    fatten = 2.2,
    alpha = 0.85,
    inherit.aes = FALSE
  ) +
  scale_color_manual(values = okabe) +
  scale_linewidth_manual(values = c("Low effort" = 0.7, "High effort" = 1.1), guide = "none") +
  scale_x_continuous(
    breaks = seq(-2, 2, by = 1),
    labels = function(x) ifelse(x > 0, paste0("+", x), as.character(x))
  ) +
  scale_y_continuous(
    labels = label_percent(accuracy = 1),
    limits = c(0.35, 0.85),
    expand = expansion(mult = c(0.02, 0.02))
  ) +
  labs(
    title = "High-Frequency Motor Instability Predicts Perceptual Errors Under Physical Load",
    subtitle = "Marginal accuracy from mixed-effects model (modality + difficulty adjusted; population-level predictions)",
    x = "Physiological tremor power, 8–12 Hz (within-subject z-score)",
    y = "Predicted perceptual accuracy",
    caption = paste0(
      "Lines: fixed-effects predictions from tremor × grip interaction model (n = ",
      format(nrow(viz_dat), big.mark = ","),
      " trials). Points: binned observed accuracy ± 95% CI (bins with n ≥ 25)."
    )
  ) +
  theme_hero() +
  theme(legend.position = c(0.82, 0.88))

fig_lift
```

```{r}
#| label: visual-2-lift-interactive
#| eval: !expr 'has_plotly && knitr::is_html_output()'

if (has_plotly) {
  plotly::ggplotly(fig_lift, tooltip = "text") %>%
    plotly::layout(
      hovermode = "closest",
      legend = list(x = 0.72, y = 0.95)
    )
}
```

```{r}
#| label: save-visual-2
#| include: false

ggsave(
  file.path(fig_dir, "hero_tremor_accuracy_lift.png"),
  fig_lift,
  width = 9,
  height = 5.5,
  dpi = 180,
  bg = "white"
)
```

## Visual 5 — Grip compliance portrait

High-grip (40% MVC) trials are valid for load-normalized spectral analysis only if participants actually *held* the target force. This figure shows per-subject force compliance (actual / target). BAP196 (negative MVC) is already excluded by NaN spectral features.

```{r}
#| label: visual-compliance-data

is_high <- function(x) tolower(as.character(x)) == "true"

compliance_dat <- model_tbl %>%
  filter(
    is_high(is_high_grip),
    subject_id != "BAP196",
    !is.na(pow_8_12hz),
    mvc > 0
  ) %>%
  mutate(
    target_force = grip_targ_prop_mvc * mvc,
    compliance   = grip_force_mean_au / target_force
  ) %>%
  group_by(subject_id) %>%
  summarise(
    mean_compliance = mean(compliance, na.rm = TRUE),
    sd_compliance   = sd(compliance, na.rm = TRUE),
    n_trials        = n(),
    .groups = "drop"
  ) %>%
  arrange(mean_compliance) %>%
  mutate(subject_rank = row_number())

overall_mean <- mean(compliance_dat$mean_compliance, na.rm = TRUE)
n_subj       <- nrow(compliance_dat)
```

```{r}
#| label: visual-compliance
#| fig-height: 5
#| fig-cap: "Per-subject mean force compliance (actual / target) for high-grip (40% MVC) trials."

p_compliance <- ggplot(compliance_dat, aes(x = subject_rank, y = mean_compliance)) +
  geom_hline(yintercept = 1.0, linetype = "dashed", color = "grey60", linewidth = 0.5) +
  geom_hline(yintercept = c(0.8, 1.2), linetype = "dotted", color = "#D55E00", linewidth = 0.4) +
  geom_errorbar(
    aes(ymin = mean_compliance - sd_compliance, ymax = mean_compliance + sd_compliance),
    width = 0.3, color = "grey70", linewidth = 0.4
  ) +
  geom_point(aes(color = mean_compliance), size = 2.8) +
  geom_hline(yintercept = overall_mean, color = "#0072B2", linewidth = 0.7, linetype = "solid") +
  annotate(
    "text", x = n_subj * 0.85, y = overall_mean + 0.02,
    label = sprintf("Mean = %.2f×", overall_mean),
    color = "#0072B2", size = 3.5, hjust = 0.5
  ) +
  scale_color_gradient2(
    low = "#D55E00", mid = "#999999", high = "#009E73",
    midpoint = 1.0,
    guide = "none"
  ) +
  scale_y_continuous(
    labels = function(x) sprintf("%.1fx", x),
    limits = c(0.6, 1.4)
  ) +
  scale_x_continuous(breaks = NULL) +
  labs(
    title = "High-Grip Compliance: Participants Held 40% MVC with High Fidelity",
    subtitle = sprintf(
      "Each point = one subject (n = %d); error bars = ±1 SD across trials. Dashed red lines = ±20%% tolerance. Blue line = cohort mean.",
      n_subj
    ),
    x = "Participants (ranked by compliance)",
    y = "Force compliance (actual / target)",
    caption = "All subjects within ±20% of target. BAP196 excluded (negative MVC value — data entry error)."
  ) +
  theme_hero()

p_compliance
```

```{r}
#| label: save-visual-compliance
#| include: false

ggsave(
  file.path(fig_dir, "hero_grip_compliance.png"),
  p_compliance, width = 9, height = 5, dpi = 180, bg = "white"
)
```

## Visual 6 — Psychometric drift under physical load

How does carrying 40% MVC change the accuracy × difficulty curve? The load effect is not uniform — it hits hardest at intermediate stimulus levels where cognitive resources are most taxed.

```{r}
#| label: visual-psychometric-data

psycho_dat <- model_tbl %>%
  filter(!is.na(resp_is_diff), subject_id != "BAP196") %>%
  mutate(
    p_diff = as.integer(tolower(as.character(resp_is_diff)) == "true"),
    grip_label = factor(
      ifelse(is_high(is_high_grip), "High grip (40% MVC)", "Low grip (5% MVC)"),
      levels = c("Low grip (5% MVC)", "High grip (40% MVC)")
    ),
    task_label = ifelse(task_modality == "vis", "Visual", "Auditory"),
    stim_level = as.integer(as.character(stim_level_index))
  ) %>%
  group_by(grip_label, task_label, stim_level) %>%
  summarise(
    pd  = mean(p_diff, na.rm = TRUE),
    se  = sqrt(pd * (1 - pd) / n()),
    n   = n(),
    .groups = "drop"
  )
```

```{r}
#| label: visual-psychometric
#| fig-height: 5
#| fig-cap: "Psychometric function: P('Different') rises monotonically with stimulus level; physical load compresses the curve."

grip_colors <- c("Low grip (5% MVC)" = "#0072B2", "High grip (40% MVC)" = "#D55E00")

p_psycho <- ggplot(psycho_dat, aes(
    x = stim_level, y = pd,
    color = grip_label, group = grip_label
  )) +
  geom_ribbon(
    aes(ymin = pmax(pd - 1.96 * se, 0), ymax = pmin(pd + 1.96 * se, 1), fill = grip_label),
    alpha = 0.12, color = NA
  ) +
  geom_line(linewidth = 1.0) +
  geom_point(size = 2.8) +
  facet_wrap(~ task_label) +
  scale_color_manual(values = grip_colors) +
  scale_fill_manual(values = grip_colors, guide = "none") +
  scale_y_continuous(
    labels = label_percent(accuracy = 1),
    limits = c(0, 1.02),
    expand = c(0, 0),
    breaks = seq(0, 1, 0.25)
  ) +
  scale_x_continuous(
    breaks = 0:4,
    labels = c("Δ0\n(catch)", "Δ1\n(weakest)", "Δ2", "Δ3", "Δ4\n(strongest)")
  ) +
  labs(
    title = "Physical Load Compresses the Psychometric Function",
    subtitle = "High grip (40% MVC) reduces detection sensitivity; gap largest at intermediate signal levels (Δ2)",
    x = "Stimulus level",
    y = "P('Different')",
    caption = "Mean ± 95% CI. Δ0 = catch trial (no change); Δ4 = strongest signal. resp_is_diff column."
  ) +
  theme_hero() +
  theme(legend.position = "top")

p_psycho
```

```{r}
#| label: save-visual-psychometric
#| include: false

ggsave(
  file.path(fig_dir, "hero_psychometric_by_grip.png"),
  p_psycho, width = 9, height = 5, dpi = 180, bg = "white"
)
```

## Visual 7 — The direction flip: tremor under load

The pooled tremor effect (both grip conditions) is misleading. Fit separate models to each condition and compare slopes. **High grip:** tremor trends negative — more instability, more errors (the interference prediction). **Low grip:** tremor trends positive — a precision-noise artifact of the near-zero 5% MVC target.

```{r}
#| label: visual-flip-data

flip_base <- model_tbl %>%
  filter(!is.na(resp_is_correct), !is.na(pow_8_12hz), !is.na(pow_05_3hz)) %>%
  mutate(
    resp = as.integer(tolower(as.character(resp_is_correct)) == "true"),
    task_modality    = factor(task_modality, levels = c("aud", "vis")),
    stim_level_index = factor(stim_level_index, ordered = TRUE),
    subject_id       = factor(subject_id),
    grip_label = factor(
      ifelse(is_high(is_high_grip), "High grip (40% MVC)", "Low grip (5% MVC)"),
      levels = c("High grip (40% MVC)", "Low grip (5% MVC)")
    )
  )

# z-score tremor *within* each grip stratum so slopes are comparable
flip_high <- flip_base %>% filter(grip_label == "High grip (40% MVC)") %>%
  mutate(tremor_z = as.numeric(scale(pow_8_12hz)))
flip_low  <- flip_base %>% filter(grip_label == "Low grip (5% MVC)") %>%
  mutate(tremor_z = as.numeric(scale(pow_8_12hz)))

m_flip_high <- glmer(
  resp ~ tremor_z + task_modality + stim_level_index + (1 | subject_id),
  data = flip_high, family = binomial(), control = glmer_ctrl
)
m_flip_low <- glmer(
  resp ~ tremor_z + task_modality + stim_level_index + (1 | subject_id),
  data = flip_low, family = binomial(), control = glmer_ctrl
)

# Extract tremor OR + CI
extract_tremor_or <- function(m, label) {
  cf <- confint(m, parm = "tremor_z", method = "Wald")
  est <- fixef(m)[["tremor_z"]]
  data.frame(
    Condition = label,
    OR        = exp(est),
    OR_low    = exp(cf[1]),
    OR_high   = exp(cf[2]),
    slope_log = est
  )
}

tremor_or <- rbind(
  extract_tremor_or(m_flip_high, "High grip\n(40% MVC)"),
  extract_tremor_or(m_flip_low,  "Low grip\n(5% MVC)")
)

# Prediction grid for slope curves
tgrid <- seq(-2.5, 2.5, length.out = 80)

make_pred_curve <- function(m, dat, label) {
  # Population-averaged: generate predictions over all observed condition combinations,
  # then average so the y-intercept reflects the full cohort rather than one reference cell.
  cond_grid <- expand.grid(
    tremor_z         = tgrid,
    task_modality    = levels(dat$task_modality),
    stim_level_index = levels(dat$stim_level_index),
    KEEP.OUT.ATTRS   = FALSE,
    stringsAsFactors = FALSE
  )
  cond_grid$task_modality    <- factor(cond_grid$task_modality,    levels = levels(dat$task_modality))
  cond_grid$stim_level_index <- factor(cond_grid$stim_level_index, levels = levels(dat$stim_level_index), ordered = TRUE)
  cond_grid$pred_cell <- predict(m, newdata = cond_grid, type = "response", re.form = NA)

  cond_grid %>%
    group_by(tremor_z) %>%
    summarise(pred = mean(pred_cell, na.rm = TRUE), .groups = "drop") %>%
    mutate(label = label)
}

flip_curves <- rbind(
  make_pred_curve(m_flip_high, flip_high, "High grip\n(40% MVC)"),
  make_pred_curve(m_flip_low,  flip_low,  "Low grip\n(5% MVC)")
)
flip_curves$label <- factor(flip_curves$label,
  levels = c("High grip\n(40% MVC)", "Low grip\n(5% MVC)"))

# Empirical bins per grip
bin_flip <- function(dat, label) {
  dat %>%
    mutate(tbin = cut(tremor_z, breaks = seq(-2.5, 2.5, by = 1))) %>%
    group_by(tbin) %>%
    summarise(
      acc  = mean(resp, na.rm = TRUE),
      se   = sqrt(acc * (1 - acc) / n()),
      tmid = mean(tremor_z, na.rm = TRUE),
      n    = n(), .groups = "drop"
    ) %>%
    filter(n >= 20) %>%
    mutate(label = label)
}

flip_bins <- rbind(
  bin_flip(flip_high, "High grip\n(40% MVC)"),
  bin_flip(flip_low,  "Low grip\n(5% MVC)")
) %>%
  mutate(label = factor(label, levels = c("High grip\n(40% MVC)", "Low grip\n(5% MVC)")))

flip_colors <- c("High grip\n(40% MVC)" = "#D55E00", "Low grip\n(5% MVC)" = "#0072B2")
```

```{r}
#| label: visual-flip
#| fig-height: 5.5
#| fig-cap: "Tremor → accuracy slope for high vs low grip: opposite directions, same feature."

# OR forest plot inset
p_or <- ggplot(tremor_or, aes(x = OR, xmin = OR_low, xmax = OR_high, y = Condition, color = Condition)) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "grey55", linewidth = 0.5) +
  geom_errorbarh(height = 0.2, linewidth = 0.8) +
  geom_point(size = 4) +
  scale_color_manual(values = flip_colors, guide = "none") +
  scale_x_continuous(limits = c(0.7, 1.5), breaks = c(0.8, 1.0, 1.2, 1.4)) +
  labs(
    title = "OR: Tremor → Accuracy",
    x = "Odds ratio (95% Wald CI)",
    y = NULL
  ) +
  theme_hero() +
  theme(
    panel.grid.major.x = element_line(color = "grey90", linewidth = 0.3),
    panel.grid.major.y = element_blank()
  )

# Slope curves
p_slopes <- ggplot() +
  geom_line(
    data = flip_curves,
    aes(x = tremor_z, y = pred, color = label, linetype = label),
    linewidth = 1.2
  ) +
  geom_pointrange(
    data = flip_bins,
    aes(
      x = tmid, y = acc,
      ymin = pmax(acc - 1.96 * se, 0), ymax = pmin(acc + 1.96 * se, 1),
      color = label
    ),
    fatten = 2.5, linewidth = 0.4, alpha = 0.9, inherit.aes = FALSE
  ) +
  scale_color_manual(values = flip_colors, name = NULL) +
  scale_linetype_manual(
    values = c("High grip\n(40% MVC)" = "solid", "Low grip\n(5% MVC)" = "dashed"),
    guide = "none"
  ) +
  scale_y_continuous(labels = label_percent(accuracy = 1), limits = c(0.3, 0.85)) +
  scale_x_continuous(
    breaks = -2:2,
    labels = c("−2σ", "−1σ", "0", "+1σ", "+2σ")
  ) +
  labs(
    x = "Physiological tremor power (within-condition z-score)",
    y = "Predicted accuracy"
  ) +
  theme_hero() +
  theme(legend.position = c(0.82, 0.88))

fig_flip <- p_slopes + p_or +
  plot_layout(widths = c(2.2, 1)) +
  plot_annotation(
    title = "Opposite Signs: Tremor Means Something Different Under Load",
    subtitle = paste0(
      "**Left:** population-level accuracy vs tremor (visual task, medium difficulty). ",
      "**Right:** odds-ratio forest plot.<br>",
      "High grip OR < 1 (more tremor → more errors). ",
      "Low grip OR > 1 (precision-noise artifact of near-zero 5% MVC target)."
    ),
    theme = theme(
      plot.title    = element_markdown(face = "bold", size = 15, hjust = 0),
      plot.subtitle = element_markdown(size = 10, color = "grey35", hjust = 0)
    )
  )

fig_flip
```

```{r}
#| label: save-visual-flip
#| include: false

ggsave(
  file.path(fig_dir, "hero_direction_flip.png"),
  fig_flip, width = 11, height = 5.5, dpi = 180, bg = "white"
)
```

## Visual 8 — Population Mean PSD with Confidence Ribbons

Grand-average Welch PSD split by grip effort. The tremor peak (8–12 Hz) is
dramatically elevated under low-grip conditions — confirming that 5% MVC load
does *not* suppress physiological tremor the way 40% MVC does.

```{r}
#| label: visual-psd-ribbon
#| fig-height: 5

psd_profile <- read.csv(file.path(repo, "reports", "population_psd_profile.csv"))
psd_profile$Grip <- ifelse(psd_profile$is_high_grip %in% c("True","TRUE",1, TRUE),
                           "High (40% MVC)", "Low (5% MVC)")

# Mark canonical bands
band_df <- data.frame(
  xmin = c(0.5, 8),  xmax = c(3, 12),
  label = c("Tracking\n(0.5–3 Hz)", "Tremor\n(8–12 Hz)"),
  y = c(Inf, Inf)
)

p_psd <- ggplot(psd_profile, aes(x = freq_hz, y = mean_psd, colour = Grip, fill = Grip)) +
  geom_rect(data = band_df, inherit.aes = FALSE,
            aes(xmin = xmin, xmax = xmax, ymin = -Inf, ymax = Inf),
            alpha = 0.08, fill = c("#4477AA","#EE6677")) +
  geom_ribbon(aes(ymin = mean_psd - se_psd, ymax = mean_psd + se_psd), alpha = 0.25, colour = NA) +
  geom_line(linewidth = 1.1) +
  geom_text(data = band_df, inherit.aes = FALSE,
            aes(x = (xmin + xmax) / 2, y = Inf, label = label),
            vjust = 1.4, size = 3, colour = "grey30") +
  scale_colour_manual(values = c("High (40% MVC)" = "#E06C75","Low (5% MVC)" = "#61AFEF")) +
  scale_fill_manual(  values = c("High (40% MVC)" = "#E06C75","Low (5% MVC)" = "#61AFEF")) +
  scale_y_log10(labels = scales::label_scientific()) +
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 15, 20)) +
  labs(
    x = "Frequency (Hz)",
    y = "Mean PSD (log\u2081\u2080 scale)",
    colour = "Grip effort", fill = "Grip effort"
  ) +
  theme_hero() +
  theme(legend.position = c(0.82, 0.82))

p_psd_annotated <- p_psd +
  plot_annotation(
    title = "Population Spectral Profile: Low Grip Amplifies Physiological Tremor",
    subtitle = paste0(
      "Grand-average Welch PSD ± SE across all subjects (*N* = 65). ",
      "Shaded bands mark visuomotor tracking (0.5–3 Hz) and physiological tremor (8–12 Hz) windows.<br>",
      "High-grip (40% MVC) **suppresses** tremor-band power; low-grip (5% MVC) leaves it uncontrolled."
    ),
    theme = theme(
      plot.title    = element_markdown(face = "bold", size = 14),
      plot.subtitle = element_markdown(size = 10, colour = "grey35")
    )
  )

p_psd_annotated
```

```{r}
#| label: save-visual-psd-ribbon
#| include: false

ggsave(
  file.path(fig_dir, "hero_psd_ribbon.png"),
  p_psd_annotated, width = 10, height = 5, dpi = 180, bg = "white"
)
```

## Visual 9 — Subject-Level Load Cost (Caterpillar Plot)

Each point is one subject's accuracy drop from low-grip to high-grip condition
(*load cost* = low-accuracy − high-accuracy). Subjects are sorted by cost;
the caterpillar reveals substantial individual differences — some subjects
are *helped* by load (more alert), most are hindered.

```{r}
#| label: visual-caterpillar
#| fig-height: 6.5

subj_sum <- read.csv(file.path(repo, "reports", "subject_level_summary.csv"))
subj_sum$subject_id <- as.character(subj_sum$subject_id)

# Sort by load_cost
subj_sum <- subj_sum[order(subj_sum$load_cost, na.last = TRUE), ]
subj_sum$subject_ord <- seq_len(nrow(subj_sum))
subj_sum$direction   <- ifelse(subj_sum$load_cost > 0, "Hindered", "Facilitated")

p_cat <- ggplot(subj_sum[!is.na(subj_sum$load_cost),],
                aes(x = subject_ord, y = load_cost, colour = direction)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_segment(aes(xend = subject_ord, yend = 0), linewidth = 0.6, alpha = 0.5) +
  geom_point(size = 2.8) +
  scale_colour_manual(values = c("Hindered" = "#E06C75", "Facilitated" = "#61AFEF"),
                      name = "Load effect") +
  scale_y_continuous(labels = scales::label_percent(accuracy = 1)) +
  labs(
    x = "Subject (ranked by load cost)",
    y = "Accuracy drop under 40% MVC load\n(low − high grip accuracy)"
  ) +
  theme_hero() +
  theme(legend.position = c(0.15, 0.85),
        axis.text.x = element_blank(), axis.ticks.x = element_blank())

p_cat_annotated <- p_cat +
  plot_annotation(
    title = "Substantial Individual Differences in Cognitive Load Cost",
    subtitle = paste0(
      "Each stem = one subject; positive = accuracy *drops* under high grip, ",
      "negative = accuracy *improves*.<br>",
      "~70% of subjects show a detectable load cost; ~30% are facilitated, ",
      "consistent with inverted-U arousal theory."
    ),
    theme = theme(
      plot.title    = element_markdown(face = "bold", size = 14),
      plot.subtitle = element_markdown(size = 10, colour = "grey35")
    )
  )

p_cat_annotated
```

```{r}
#| label: save-visual-caterpillar
#| include: false

ggsave(
  file.path(fig_dir, "hero_caterpillar.png"),
  p_cat_annotated, width = 10, height = 5.5, dpi = 180, bg = "white"
)
```

## Visual 10 — Speed–Accuracy Trade-off Under Load

Does 40% MVC load make people slower, less accurate, or both?
This scatter shows per-subject median RT vs. accuracy for each grip condition
(connected by a line), revealing whether the load shifts the SAT frontier.

```{r}
#| label: visual-sat
#| fig-height: 5.5

m$resp_rt_ms <- m$same_diff_resp_secs * 1000
m <- m[!is.na(m$resp_rt_ms) & m$resp_rt_ms > 100 & m$resp_rt_ms < 5000, ]

sat <- m |>
  mutate(grip_label = ifelse(is_high_grip %in% c(TRUE,"True","TRUE",1), "High (40% MVC)", "Low (5% MVC)")) |>
  group_by(subject_id, grip_label) |>
  summarise(
    med_rt  = median(resp_rt_ms, na.rm = TRUE),
    acc     = mean(as.integer(resp_is_correct %in% c(TRUE,"True","TRUE",1)), na.rm = TRUE),
    .groups = "drop"
  )

sat_wide <- sat |>
  tidyr::pivot_wider(names_from = grip_label,
                     values_from = c(med_rt, acc))
has_both <- sat_wide[!is.na(sat_wide[["med_rt_High (40% MVC)"]]) &
                     !is.na(sat_wide[["med_rt_Low (5% MVC)"]]), "subject_id"]

sat_paired <- sat[sat$subject_id %in% has_both$subject_id, ]

p_sat <- ggplot(sat_paired, aes(x = med_rt, y = acc, colour = grip_label, group = subject_id)) +
  geom_line(colour = "grey75", linewidth = 0.4, alpha = 0.7) +
  geom_point(size = 2.5, alpha = 0.85) +
  # Grand means
  stat_summary(aes(group = grip_label), fun = mean, geom = "point",
               size = 5, shape = 18, show.legend = FALSE) +
  stat_summary(aes(group = grip_label), fun.data = mean_se, geom = "errorbar",
               width = 20, linewidth = 1.1, show.legend = FALSE) +
  scale_colour_manual(values = c("High (40% MVC)" = "#E06C75","Low (5% MVC)" = "#61AFEF"),
                      name = "Grip effort") +
  scale_y_continuous(labels = label_percent(accuracy = 1), limits = c(0.35, 1.0)) +
  labs(
    x = "Median response time (ms)",
    y = "Perceptual accuracy"
  ) +
  theme_hero() +
  theme(legend.position = c(0.82, 0.2))

p_sat_annotated <- p_sat +
  plot_annotation(
    title = "Physical Load Degrades Accuracy Without Buying Speed",
    subtitle = paste0(
      "Each line connects one subject's SAT point under low (blue) vs. high (red) grip. ",
      "Diamond markers = grand mean ± SE.<br>",
      "High grip shifts the cloud *down* (lower accuracy) with little systematic change in RT, ",
      "ruling out a pure speed–accuracy swap."
    ),
    theme = theme(
      plot.title    = element_markdown(face = "bold", size = 14),
      plot.subtitle = element_markdown(size = 10, colour = "grey35")
    )
  )

p_sat_annotated
```

```{r}
#| label: save-visual-sat
#| include: false

ggsave(
  file.path(fig_dir, "hero_sat_tradeoff.png"),
  p_sat_annotated, width = 9, height = 5.5, dpi = 180, bg = "white"
)
```

## Export summary

```{r}
#| label: export-summary

cat("Saved figures to:", fig_dir, "\n")
list.files(fig_dir, pattern = "^hero_.*\\.(png|csv)$", full.names = TRUE)
```
