---
title: "BAP Gripforce — Hero Visualizations"
author: "Mohd Dastgheib"
format:
  html:
    toc: true
    code-tools: true
    code-fold: true
    code-summary: "View the underlying logic"
    theme: cosmo
    fig-width: 9
    fig-height: 10
execute:
  warning: false
  message: false
fig-format: png
fig-dpi: 180
---

## Overview

Portfolio-grade figures for quantitative UX / human-factors audiences:

1. **Single-trial anatomy** — raw force, target-centered error, and rolling instability with probe-onset shading.
2. **Behavioral lift** — adjusted accuracy as a function of tremor-band power, split by grip effort.

Inputs: `reports/analysis_trial_table.csv` plus raw grip CSVs via `config/paths.local.yaml`.

```{r}
#| label: install-packages
#| eval: false

install.packages(c(
  "ggplot2", "patchwork", "ggtext", "dplyr", "tidyr",
  "scales", "lme4", "yaml", "stringr", "plotly", "htmlwidgets"
))
```

```{r}
#| label: setup

suppressPackageStartupMessages({
  library(ggplot2)
  library(patchwork)
  library(ggtext)
  library(dplyr)
  library(tidyr)
  library(scales)
  library(lme4)
  library(yaml)
  library(stringr)
})

has_plotly <- requireNamespace("plotly", quietly = TRUE) &&
  requireNamespace("htmlwidgets", quietly = TRUE)

repo <- normalizePath("..", winslash = "/", mustWork = TRUE)
if (!file.exists(file.path(repo, "reports", "analysis_trial_table.csv"))) {
  repo <- normalizePath(".", winslash = "/", mustWork = TRUE)
}

config_path <- file.path(repo, "config", "paths.local.yaml")
if (!file.exists(config_path)) {
  config_path <- file.path(repo, "config", "paths.example.yaml")
}
paths <- read_yaml(config_path)
grip_root <- paths[["gripforce_root"]]
model_path <- file.path(repo, "reports", "analysis_trial_table.csv")
fig_dir <- file.path(repo, "reports", "figures")
dir.create(fig_dir, recursive = TRUE, showWarnings = FALSE)

fs_hz <- 100
trial_epoch_s <- 2.94
probe_window_s <- 0.15

okabe <- c(
  "Low effort" = "#0072B2",
  "High effort" = "#D55E00"
)

theme_hero <- function(base_size = 12) {
  theme_minimal(base_size = base_size) +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.major.y = element_line(color = "grey90", linewidth = 0.35),
      plot.title = element_markdown(face = "bold", size = rel(1.15), hjust = 0),
      plot.subtitle = element_markdown(color = "grey35", size = rel(0.95), hjust = 0),
      plot.caption = element_text(color = "grey45", size = rel(0.78), hjust = 0),
      axis.title = element_text(color = "grey15", face = "plain"),
      axis.text = element_text(color = "grey25"),
      legend.position = "top",
      legend.title = element_blank(),
      plot.margin = margin(12, 16, 12, 12)
    )
}

probe_rect <- function(stim_onset_s, width_s = probe_window_s) {
  annotate(
    "rect",
    xmin = stim_onset_s,
    xmax = stim_onset_s + width_s,
    ymin = -Inf,
    ymax = Inf,
    fill = "#FFB000",
    alpha = 0.18
  )
}

panel_tag <- function(label) {
  annotate(
    "text",
    x = -Inf, y = Inf,
    label = label,
    hjust = -0.15, vjust = 1.35,
    fontface = "bold",
    size = 4.2,
    color = "grey20"
  )
}

rolling_var <- function(x, window = 31) {
  n <- length(x)
  half <- window %/% 2
  vapply(seq_len(n), function(i) {
    lo <- max(1L, i - half)
    hi <- min(n, i + half)
    stats::var(x[lo:hi], na.rm = TRUE)
  }, numeric(1))
}

find_grip_file <- function(subject_id, session_num, run_num, task, root) {
  pattern <- sprintf(
    "subject%s_%s_session%s_run%s_.*_gripforce\\.csv",
    subject_id, task, session_num, run_num
  )
  hits <- list.files(root, pattern = pattern, full.names = TRUE, recursive = TRUE)
  if (length(hits) == 0) {
    stop("No gripforce file found for ", subject_id, " ", task, " session ", session_num)
  }
  hits[[1]]
}

load_trial_trace <- function(
    subject_id,
    session_num,
    run_num,
    trial_idx,
    task,
    mvc,
    grip_targ_prop_mvc,
    stim_offset_s,
    root = grip_root,
    fs = fs_hz,
    min_rows_per_trial = 100) {
  path <- find_grip_file(subject_id, session_num, run_num, task, root)
  raw <- read.csv(
    path,
    header = FALSE,
    col.names = c("marker", "elapsed_time", "abs_time", "raw_force")
  )

  task_upper <- toupper(task)
  raw$grip_force_au <- if (task_upper %in% c("AODDBALL", "VODDBALL")) {
    raw$marker
  } else {
    raw$raw_force
  }

  raw$epoch_idx <- cumsum(c(1, diff(raw$elapsed_time) < 0))
  counts <- raw %>%
    count(epoch_idx, name = "n_rows")
  keep_epochs <- counts %>%
    filter(n_rows >= min_rows_per_trial) %>%
    arrange(epoch_idx) %>%
    mutate(trial_idx = row_number())

  trial <- raw %>%
    inner_join(keep_epochs %>% select(epoch_idx, trial_idx), by = "epoch_idx") %>%
    filter(trial_idx == !!trial_idx) %>%
    arrange(elapsed_time)

  if (nrow(trial) < 50) {
    stop(
      "Trial ", trial_idx, " in ", basename(path),
      " has too few samples after segmentation (", nrow(trial), ")."
    )
  }

  trial$t_rel_s <- trial$elapsed_time - trial$elapsed_time[1]
  target_force <- grip_targ_prop_mvc * mvc
  trial$target_force <- target_force
  trial$normalized_error <- (trial$grip_force_au - target_force) / target_force
  trial$rolling_var <- rolling_var(trial$normalized_error, window = 31)
  trial$stim_onset_s <- stim_offset_s

  trial
}
```

## Visual 1 — Single-trial anatomy (time domain)

```{r}
#| label: visual-1-data

model_tbl <- read.csv(model_path, stringsAsFactors = FALSE)

hero_meta <- model_tbl %>%
  filter(
    task_modality == "vis",
    tolower(as.character(is_high_grip)) == "true",
    tolower(as.character(resp_is_correct)) == "false",
    !is.na(pow_8_12hz)
  ) %>%
  arrange(desc(pow_8_12hz)) %>%
  slice(1)

trace <- load_trial_trace(
  subject_id = hero_meta$subject_id,
  session_num = hero_meta$session_num,
  run_num = hero_meta$run_num,
  trial_idx = hero_meta$trial_idx,
  task = hero_meta$task,
  mvc = hero_meta$mvc,
  grip_targ_prop_mvc = hero_meta$grip_targ_prop_mvc,
  stim_offset_s = hero_meta$probe_onset_s   # seconds into trial; NOT stim_offset for aud
)

trace_label <- sprintf(
  "%s · %s · session %s · trial %s · incorrect response",
  hero_meta$subject_id,
  hero_meta$task_modality,
  hero_meta$session_num,
  hero_meta$trial_idx
)
```

```{r}
#| label: visual-1-anatomy
#| fig-cap: "Single-trial grip-force anatomy aligned to probe onset."

p_force <- ggplot(trace, aes(x = t_rel_s, y = grip_force_au)) +
  geom_line(color = "#0072B2", linewidth = 0.75) +
  geom_hline(
    yintercept = hero_meta$grip_targ_prop_mvc * hero_meta$mvc,
    linetype = "dashed",
    color = "#999999",
    linewidth = 0.45
  ) +
  probe_rect(hero_meta$stim_offset) +
  panel_tag("A") +
  scale_x_continuous(limits = c(0, trial_epoch_s), expand = c(0, 0)) +
  labs(
    x = NULL,
    y = "Grip force (a.u.)"
  ) +
  theme_hero()

p_error <- ggplot(trace, aes(x = t_rel_s, y = normalized_error)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "#666666", linewidth = 0.45) +
  geom_line(color = "#009E73", linewidth = 0.75) +
  probe_rect(hero_meta$stim_offset) +
  panel_tag("B") +
  scale_x_continuous(limits = c(0, trial_epoch_s), expand = c(0, 0)) +
  labs(
    x = NULL,
    y = "Normalized error  (F - F_target) / F_target"
  ) +
  theme_hero()

p_instability <- ggplot(trace, aes(x = t_rel_s, y = rolling_var)) +
  geom_line(color = "#D55E00", linewidth = 0.8) +
  probe_rect(hero_meta$stim_offset) +
  panel_tag("C") +
  scale_x_continuous(limits = c(0, trial_epoch_s), expand = c(0, 0)) +
  scale_y_continuous(labels = label_number(accuracy = 0.001)) +
  labs(
    x = "Time within trial (s)",
    y = "Rolling variance\n(instability)"
  ) +
  theme_hero()

fig_anatomy <- p_force / p_error / p_instability +
  plot_annotation(
    title = "Single-Trial Grip Dynamics During Perceptual Decision",
    subtitle = paste0(
      trace_label,
      "<br>Shaded band = probe onset window (*stim_offset* = ",
      format(hero_meta$stim_offset, nsmall = 2),
      " s); dashed line in **A** = grip target."
    ),
    theme = theme(
      plot.title = element_markdown(face = "bold", size = 16, hjust = 0),
      plot.subtitle = element_markdown(size = 11, color = "grey35", hjust = 0)
    )
  )

fig_anatomy
```

```{r}
#| label: visual-1-anatomy-interactive
#| eval: !expr 'has_plotly && knitr::is_html_output()'

if (has_plotly) {
  plotly::subplot(
    plotly::ggplotly(p_force, tooltip = "text") %>%
      plotly::layout(hovermode = "x unified"),
    plotly::ggplotly(p_error, tooltip = "text") %>%
      plotly::layout(hovermode = "x unified"),
    plotly::ggplotly(p_instability, tooltip = "text") %>%
      plotly::layout(hovermode = "x unified"),
    nrows = 3,
    shareX = TRUE,
    titleY = TRUE
  ) %>%
    plotly::layout(
      title = list(
        text = paste0(
          "Single-Trial Grip Dynamics During Perceptual Decision<br>",
          "<sup>", trace_label, " · hover to inspect time points</sup>"
        ),
        x = 0.01,
        xanchor = "left"
      ),
      showlegend = FALSE
    )
}
```

```{r}
#| label: save-visual-1
#| include: false

ggsave(
  file.path(fig_dir, "hero_single_trial_anatomy.png"),
  fig_anatomy,
  width = 9,
  height = 10,
  dpi = 180,
  bg = "white"
)
```

## Visual 2 — Behavioral lift (DSP × effort)

Adjusted marginal accuracy from a mixed model with tremor × grip interaction, controlling for modality and difficulty.

```{r}
#| label: visual-2-data

viz_dat <- model_tbl %>%
  filter(
    !is.na(resp_is_correct),
    !is.na(pow_8_12hz),
    !is.na(pow_05_3hz)
  ) %>%
  mutate(
    resp_is_correct = as.integer(tolower(as.character(resp_is_correct)) == "true"),
    task_modality = factor(task_modality, levels = c("aud", "vis")),
    stim_level_index = factor(stim_level_index, ordered = TRUE),
    grip_effort = factor(
      tolower(as.character(is_high_grip)) == "true",
      levels = c(FALSE, TRUE),
      labels = c("Low effort", "High effort")
    ),
    subject_id = factor(subject_id),
    tremor_z = as.numeric(scale(pow_8_12hz))
  )

glmer_ctrl <- glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

m_lift <- glmer(
  resp_is_correct ~ tremor_z * grip_effort + task_modality + stim_level_index +
    (1 | subject_id),
  data = viz_dat,
  family = binomial(),
  control = glmer_ctrl
)

tremor_grid <- seq(-2, 2, length.out = 60)
pred_grid <- expand.grid(
  tremor_z = tremor_grid,
  grip_effort = levels(viz_dat$grip_effort),
  task_modality = "vis",
  stim_level_index = factor(2, levels = levels(viz_dat$stim_level_index), ordered = TRUE),
  KEEP.OUT.ATTRS = FALSE,
  stringsAsFactors = FALSE
)
pred_grid$grip_effort <- factor(pred_grid$grip_effort, levels = levels(viz_dat$grip_effort))
pred_grid$task_modality <- factor(pred_grid$task_modality, levels = levels(viz_dat$task_modality))

pred_grid$pred_acc <- predict(m_lift, newdata = pred_grid, type = "response", re.form = NA)

# Empirical bins for overlay
viz_bins <- viz_dat %>%
  mutate(tremor_bin = cut(
    tremor_z,
    breaks = seq(-2.5, 2.5, by = 1),
    labels = c("< −1.5", "−1.5 to −0.5", "−0.5 to 0.5", "0.5 to 1.5", "> 1.5")
  )) %>%
  group_by(grip_effort, tremor_bin) %>%
  summarise(
    acc = mean(resp_is_correct),
    se = sqrt(acc * (1 - acc) / n()),
    tremor_mid = mean(tremor_z),
    n = n(),
    .groups = "drop"
  ) %>%
  filter(n >= 25)
```

```{r}
#| label: visual-2-lift
#| fig-cap: "Population-level accuracy as a function of tremor-band power, split by grip effort."

fig_lift <- ggplot() +
  geom_line(
    data = pred_grid,
    aes(x = tremor_z, y = pred_acc, color = grip_effort, linewidth = grip_effort)
  ) +
  geom_pointrange(
    data = viz_bins,
    aes(x = tremor_mid, y = acc, ymin = pmax(acc - 1.96 * se, 0), ymax = pmin(acc + 1.96 * se, 1),
        color = grip_effort),
    linewidth = 0.35,
    fatten = 2.2,
    alpha = 0.85,
    inherit.aes = FALSE
  ) +
  scale_color_manual(values = okabe) +
  scale_linewidth_manual(values = c("Low effort" = 0.7, "High effort" = 1.1), guide = "none") +
  scale_x_continuous(
    breaks = seq(-2, 2, by = 1),
    labels = function(x) ifelse(x > 0, paste0("+", x), as.character(x))
  ) +
  scale_y_continuous(
    labels = label_percent(accuracy = 1),
    limits = c(0.35, 0.85),
    expand = expansion(mult = c(0.02, 0.02))
  ) +
  labs(
    title = "High-Frequency Motor Instability Predicts Perceptual Errors Under Physical Load",
    subtitle = "Marginal accuracy from mixed-effects model (modality + difficulty adjusted; population-level predictions)",
    x = "Physiological tremor power, 8–12 Hz (within-subject z-score)",
    y = "Predicted perceptual accuracy",
    caption = paste0(
      "Lines: fixed-effects predictions from tremor × grip interaction model (n = ",
      format(nrow(viz_dat), big.mark = ","),
      " trials). Points: binned observed accuracy ± 95% CI (bins with n ≥ 25)."
    )
  ) +
  theme_hero() +
  theme(legend.position = c(0.82, 0.88))

fig_lift
```

```{r}
#| label: visual-2-lift-interactive
#| eval: !expr 'has_plotly && knitr::is_html_output()'

if (has_plotly) {
  plotly::ggplotly(fig_lift, tooltip = "text") %>%
    plotly::layout(
      hovermode = "closest",
      legend = list(x = 0.72, y = 0.95)
    )
}
```

```{r}
#| label: save-visual-2
#| include: false

ggsave(
  file.path(fig_dir, "hero_tremor_accuracy_lift.png"),
  fig_lift,
  width = 9,
  height = 5.5,
  dpi = 180,
  bg = "white"
)
```

## Export summary

```{r}
#| label: export-summary

cat("Saved figures to:", fig_dir, "\n")
list.files(fig_dir, pattern = "^hero_.*\\.png$", full.names = TRUE)
```
